Evolutionary market ecologies \\ Model \& Numerical experiments

### 2021-06-08 draft.tex
Updates from Overleaf

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{hyperref}
\usepackage{xcolor}
\newcommand{\code}{\texttt}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\section{Preamble: baseline configuration}

Necessary condition: running GA with complete market structure
Objective: be as close as possible to Maarten's paper configuration, notably for market environment parameters.
Add Agent leverage, aggressiveness of response to be closer to Maarten
\section{Preamble 2: observables}

Necessary condition: running GA with complete market structure
To implement:
\begin{itemize}
    \item Observe market dynamics over time (easy): price, returns, assets, volatility, dividends, profits
    \item Observe ecology dynamics over time (hard): proportions? heatmap? Add entropy?
    Perhaps H (for max time horizon) plots with clear color codes (like jet) over time, and hopefully we see something clear happen.
    \item Develop a GUI or something nice/updating itself over time to observe that?
\end{itemize}

\section{Trend follower market ecology}

Necessary condition: a running GA with a single asset, market clearing, and adequate starting conditions, and the baseline configuration.

\subsection{Influence of learning vs non-learning}
The non-lerning case (replacement dynamics only) can be illustrated with:
\begin{itemize}
    \item No selection (selection rate equal to 0)
    \item No crossover (crossover rate equal to 0)
    \item No mutation (mutation rate equal to 0)
\end{itemize}
The objective is to assess the behavior of the model in this no-learning setup, establish a benchmark.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{hyperref}
\usepackage{xcolor}
\newcommand{\code}{\texttt}
\usepackage[
backend=biber,
style=alphabetic,
sorting=ynt
]{biblatex}
\addbibresource{bibliography.bib}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\usepackage{algorithm}% http://ctan.org/pkg/algorithms 
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx 
\newcommand{\var}[1]{{\ttfamily#1}}% variable

@@

% Necessary condition: running GA with complete market structure
% To implement:
% \begin{itemize}
%     \item Observe market dynamics over time (easy): price, returns, assets, volatility, dividends, profits
%     \item Observe ecology dynamics over time (hard): proportions? heatmap? Add entropy?
%     Perhaps H (for max time horizon) plots with clear color codes (like jet) over time, and hopefully we see something clear happen.
%     \item Develop a GUI or something nice/updating itself over time to observe that?
% \end{itemize}

% \section{Trend follower market ecology}

% Necessary condition: a running GA with a single asset, market clearing, and adequate starting conditions, and the baseline configuration.

The non-lerning case (replacement dynamics only) can be illustrated with:
\begin{itemize}
    \item No selection (selection rate equal to 0)
    \item No crossover (crossover rate equal to 0)
    \item No mutation (mutation rate equal to 0)
\end{itemize}
The objective is to assess the behavior of the model in this no-learning setup, establish a benchmark.
